%------------------------------------正文开始----------------------------------------------
\section{M2M Traffic Characterization}
\label{sec:overview-diff-traffic}
A comprehensive comparison between MTC and HTC is resumed in Table~\ref{tab:differences between M2M and H2H}.
The illustration of this difference helps to rethink the design of some principles and the optimization guidelines.
Some explanations about Table \ref{tab:differences between M2M and H2H}: 
\begin{itemize}[leftmargin=*, noitemsep]
	\item First, the representative device in H2H communication is smartphone, which is equipped with more and more computational capacity. The complexity of M2M devices is various: in application such as remote monitoring, it could be in format of sensor with transceiver and simplified processor. In Intelligent Transport System (ITS), it could be regarded as a smartphone without screen.
	\item Second, the experiment results in \cite{FirstLook12} reveal that compared to H2H communication, cellular M2M traffic suffers from a higher packet loss ratio, and the reason may be the adverse deployment location and the lack of UI (e.g., screen) to show the signal strength in its place. 
	\item Third, since at present, a majority of cellular M2M applications are based on GSM/UMTS technologies, MTC mainly supports SMS or data reporting service. We could imagine more innovation M2M services when 4G networks even 5G networks are largely rolled out.
\end{itemize}

Not all MTC applications have the same characteristics and not every optimization is suitable to all applications; therefore, features are defined to provide some structure to the customer and the network is then tuned accordingly to needs.

%shown in Tab.~{3GPP-MTC-feature} \cite{bartoli2011low}.
% "90% of the M2M devices across all applications are stationary" from Chapter 1.4.1.3 of book : M2M communications: a system approach
\input{Chapter2/Tables/MTC-traffic-features.tex}