\chapter{Performance Evaluation of S-ALOHA in context of single Base Station}
\label{chapter:icc17}
% **************************** Define Graphics Path **************************
\ifpdf
    \graphicspath{{Chapter4/Figs/Raster/}{Chapter4/Figs/PDF/}{Chapter4/Figs/}}
\else
    \graphicspath{{Chapter4/Figs/Vector/}{Chapter4/Figs/}}
\fi
\qs{Based on ICC2017}
The S-ALOHA (i.e. slotted-ALOHA) protocol is recently regaining interest in Low Power Wide Area Networks (LPWAN) handling M2M traffic. Despite intensive studies since the birth of S-ALOHA, the special features of M2M traffic and requirements highlight the importance of analytical models taking into account performance-affecting factors and giving a thorough performance evaluation. In this chapter, we propose a low-complexity but still accurate analytical model capable of evaluating S-ALOHA in terms of packet loss rate, throughput, energy-efficiency and average number of transmissions. The proposed model is able to facilitate dimensioning and design of S-ALOHA based LPWAN. 

This chapter is organized as follows: Sec.~\ref{sec:icc17-introduction} is the introduction part. Sec.~\ref{sec:icc17-system-model} presents the system model. Sec.~\ref{sec:ideal_power_control} is the performance analysis about S-ALOHA in ideal systems, i.e., without power control and fading. Sec.~\ref{sec:imperfect-power-control} takes into account imperfect power control under wide-band system. Sec.~\ref{sec:simulation_result} proves the accuracy of proposed model by simulation and gives some deduced design guidelines. Sec.~\ref{sec:icc17-conclusion}concludes this chapter.

\input{Chapter4/icc17_introduction}
\input{Chapter4/icc17_sota}
\input{Chapter4/icc17_system_model}
\input{Chapter4/icc17_ideal_power_control}
\input{Chapter4/icc17_imperfect_power_control} 
\input{Chapter4/icc17_fading_imperfect_power_control}
\input{Chapter4/icc17_simulation}
\input{Chapter4/icc17_conclusion}




