\section{Conclusion and Future works}
\label{sec:icc17-conclusion}
In this chapter, we have presented an accurate analytical model to evaluate the performance of S-ALOHA based LPWAN networks. By the proposed analytical model, we can estimate steady-state performances such as packet loss rate, throughput, energy efficiency and average number of transmissions. The model accounts for various performance-affecting factors, such as capture effect, diversity of transmit power levels, power control error, which have not been jointly considered in previous researches and can not be handled by widely used Bianchi's model.

We employ numerical integration method to calculate cumulative distribution function (CDF) of total interference from its corresponding characteristic function and fixed point analysis to solve the problem. The computational complexity is reduced by combining the recent research effort about log-normal sum (LNS) approximation problem and mathematical skills used in finance domain. The accuracy of the proposed model is confirmed by simulation. Due to its low complexity, our model can be used as a dimensioning tool to accurately and rapidly estimate the steady-state system outage capacity and throughput of  S-ALOHA-based LPWAN networks. 

From our proposed models, we also obtain some design guidelines for S-ALOHA. For example, in a wideband LPWAN system that suffering from imperfect power control, if the deployed devices use identical transmit power strategy and capture ratio is high such as $3$ dB, the imprecision of power control has a positive impact for a S-ALOHA based network, but has a negative impact for system that use incremental or decremental transmit power strategy. 
%Note: Our proposed model also enables to study the case where the power increment factor is a random number.
%Our proposed model is also easy to be extended to multichannel case.
%
%In this paper, we develop a systematic framework to study the 
%
%For transmit power diversity strategies, we consider three strategies: blablabla... We also study the power control impact.
%The contributions of this paper are:
%\begin{inparaenum}[1)]
%	\item propose an iterative analytical framework taking into account capture effect, power control error and diversity of transmit power level, 
%	%	different from \qs{We have not used the popular Markovian technique, i.e., Bianchi model, to analyze the steady state performance. We just use a fixed point analysis to get a steady state probability vector (detailed in system model part), which allows us to get some performance metrics such as packet loss rate, throughput, expected number of a packet delivered, etc. In my opinion, one limitation of Bianchi model and its derivaties is not able (or is very complicated if be able to do this) to process the case where transmission failure probability is different for each transmission. The advantage of our method is, we just concern how to use computer to get the target probability vector. Once we got this probability vector, other performance metrics can be easily calculated. Maybe be better to be done at last step...}largely used Markovian technique to analyze the steady state packet loss rate based on Poisson's split theorem. The analytical framework can be used to dimension the LPWAN networks with low computational complexity.
%	\item employ the recent research effort about log-normal distribution type variable approximation and mathematical skills largely used in finance domain to reduce the computational complexity;
%\end{inparaenum} 
%From the exploitation of the proposed analytical model, we observe that:
%Within a network employing identical transmit power strategy, 
%
%One possible use case: when the network is in congestion states, the devices are indicated to use incremental transmit strategy. When the congestion level are reduced, use again the identical strategy to seek for energy efficiency.
In this work, the impact of the location of deployed MTC devices are not considered. Thus, We will also take into account the impact of device's spatial distribution and multiple base stations in the future work.